Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex

 	 Other methods had low accuracy 
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledgebase}
	\subsection{Supervised LSA}
	Our approach uses simple LSA with a supervised learning component.

@@

>>>>

 	 Other methods had low accuracy 
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledgebase}
        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
        Lesk
        Semantic similarity
	\subsection{Supervised LSA}
	Our approach uses simple LSA with a supervised learning component.

@@

	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. http://wordnet.princeton.edu.

	10. R. Navigli. Word Sense Disambiguation: a Survey. ACM Computing Surveys, 41(2), ACM Press, 2009, pp. 1-69. [A complete State of the Art in Word Sense Disambiguation]

	\section{Code}

	The code we used in this paper is available at https://github.com/alee101/wsd.
